Manuscript

### 2016-07-09 inst/simulation/manuscript.Rmd
...

  p <- p + facet_wrap(~modelName) +
    scale_x_continuous(limits=xlim, labels=trans_format("identity", math_format(10^.x))) +
    scale_y_continuous(limits=ylim, labels=trans_format("identity", math_format(10^.x))) +
    xlab("True population size") + ylab("Estimated population size") +
    theme_ms2() + theme(panel.border=element_rect(fill="transparent"),
                                        plot.title=element_text(size=10),
                                        legend.margin=unit(0, units="line"),
                                        panel.margin=unit(0, units="line"))

>>>>

  p <- p + facet_wrap(~modelName) +
    scale_x_continuous(limits=xlim, labels=trans_format("identity", math_format(10^.x))) +
    scale_y_continuous(limits=ylim, labels=trans_format("identity", math_format(10^.x))) +
    xlab("True population size") + ylab("Estimated population size") +
    theme_ms2() + theme(panel.border=element_rect(fill="transparent"),
                                        plot.title=element_text(size=10),
                                        legend.margin=unit(0, units="line"))
